Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-05-31 writeup/gz_hubble_data.tex
CJL last small edits

%\usepackage{epsfig}
\usepackage{color,soul}
%\usepackage{natbib}
\usepackage{deluxetable}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{url}
%\usepackage[normalem]{ulem}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

\author[Willett et al.]{
Kyle W. Willett$^{1,2}$,
Melanie A. Galloway$^{1}$,
Steven P. Bamford$^{3}$,
Chris J. Lintott$^{4}$,
\newauthor
Karen L. Masters$^{5,6}$,
Claudia Scarlata$^{1}$,
B.D. Simmons$^{4,7}$\footnote{Einstein Fellow},
Melanie Beck$^{1}$,
\newauthor
Carolin N. Cardamone$^{8}$,
Edmond Cheung$^{9}$,
Edward M. Edmondson$^{5}$,
Lucy F. Fortson$^{1}$,
\newauthor
Roger L. Griffith$^{10,11}$,
Boris H\"au{\ss}ler$^{4,12,13}$,
Anna Han$^{14}$,
Ross Hart$^{3}$,
\newauthor
Thomas Melvin$^{5}$,
Michael Parrish$^{15}$,
Kevin Schawinski$^{16}$,
R.J. Smethurst$^{4}$,
\newauthor
Arfon M. Smith$^{4,15,17}$
\\
%
$^{1}$School of Physics and Astronomy, University of Minnesota, 116 Church St. SE, Minneapolis, MN 55455, USA \\
$^{2}$Department of Physics and Astronomy, University of Kentucky, 505 Rose St., Lexington, KY 40506, USA \\
$^{3}$School of Physics and Astronomy, The University of Nottingham, University Park, Nottingham, NG7 2RD, UK \\
$^{4}$Oxford Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK \\
$^{5}$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
$^{6}$SEPnet, South East Physics Network, UK \\
$^{7}$Center for Astrophysics and Space Sciences, Department of Physics, University of California, San Diego, CA 92093, USA \\
$^{8}$Department of Mathematics and Science, Wheelock College, Boston, MA 02215, USA \\
$^{9}$Kavli Institute for the Physics and Mathematics of the Universe (WPI), \\ Todai Institutes for Advanced Study, The University of Tokyo, Kashiwa 277-8583, Japan \\
$^{10}$Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA \\
$^{11}$Department of Astronomy \& Astrophysics, 525 Davey Lab, The Pennsylvania State University, University Park, PA 16802, USA \\
$^{12}$Centre for Astrophysics, Science \& Technology Research Institute, University of Hertfordshire, Hatfield, AL10 9AB, UK \\
$^{13}$European Southern Observatory, Alonso de C\'ordova 3107, Vitacura, Casilla 19001, Santiago, Chile \\
$^{14}$Department of Astronomy, Yale University, New Haven, CT 06520, USA \\
$^{15}$Adler Planetarium, 1300 S. Lake Shore Drive, Chicago, IL 60605, USA \\
$^{16}$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland \\
$^{17}$GitHub
}

@@

\begin{abstract}
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various publicly-released \textit{Hubble Space Telescope}
Legacy programs using the Advanced Camera for Surveys, with filters that probe
the rest-frame optical emission from galaxies out to $z\sim1$.  The bulk of the
sample is selected to have $m_{I814W}<23.5$, but goes as faint as
$m_{I814W}<26.8$ for deep images combined over 5~epochs. The median redshift of
the combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out
to $z\simeq4$. The GZH morphological data include measurements of both bulge-
and disk-dominated galaxies, details on spiral disk structure that relate to
the Hubble type, bar identification, and numerous measurements of clump
identification and geometry.  This paper also describes a new method for
calibrating morphologies for galaxies of different luminosities and at
different redshifts by using artificially-redshifted galaxy images as a
baseline. The GZH catalog contains both raw and calibrated morphological vote
fractions for $119,849$~galaxies, providing the largest dataset to date
suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
% Number = hubble + goods_shallow + stripe82_coadd
\end{abstract}

@@

The advent of larger telescopes in an increasing range of observing wavelengths
has revealed that the distribution and properties of galaxy morphology have
strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$
(roughly 6~Gyr after the Big Bang), many galaxies are still in the process of
assembling the baryonic mass required to reproduce the mature, coherent
structures seen in the present day. This growth occurs in a variety of
pathways, including accretion of baryons from large-scale galactic filaments
onto halos via streaming, mergers of individual dark matter halos along with
their baryons, conversion of gas into stars through gravitational collapse and
star formation, etc. The process can also be slowed or even reversed via
feedback from stellar winds, supernovae, and active black holes.  Each of these
processes affects the galaxy morphology in different ways, and so an accurate
measurement of the demographics as a function of redshift provides an extremely
powerful observational constraint on the physics involved \citep[for recent
reviews see][]{but13,con14}.

@@

Space-based observatories, particularly the \hubble{} (\hst), have been
responsible for the bulk of imaging studies of high-redshift galaxies.
Observations of fields with very deep imaging
\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
providing the angular resolution to distinguish internal structure and
characterize the morphology. While these measurements are helped by the fact
that the angular diameter distance is relatively flat beyond $z>1$ in a flat
$\Lambda$CDM cosmology, the relevant angular scales are only of the order
$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
much of the structure for a Milky Way-sized galaxy out to moderately high
redshifts (at least distinguishing a disk from a bulge), but is limited for
more compact structures. Since the size of galaxies evolves as roughly
$r\propto(1+z)^{-1}$ \citep{mao98,law12a}, the compact sizes of high-redshift
galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
However, the public availability of more than $10^5$~galaxies in archival
imaging has generated a data sample with the potential
for statistically-robust studies of galaxy demographics and evolution.

@@

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
    covered two separate fields in the northern and southern hemispheres: the Hubble
    Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
    \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South
    ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{}
    ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
    respectively. ACS imaging in GOODS fields used 4~filters -- F435W (\Bband),
    \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
    epoch varied by band, from 1050--2100~seconds. The \Bband{} images were completed
    in a single epoch at the beginning of the survey, but the \Vband, \iband, and
    \zband{} images were taken in five separate epochs separated by 40--50~days
    each. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
    $5\sigma$ limiting magnitude for extended sources was 25.7 for \Vband{} and
    25.0 for \iband.

@@

%Selection of galaxies from these samples is described in Section \ref{ssec:galselect} below. 
In the ACS-GC \citep{gri12}, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
GOODS-S (2-epoch), and GOODS-N (2-epoch) surveys, respectively. The full-depth
GOODS images from both fields included galaxies with $m<26.8$. This yielded a
total of $119,849$~images (Table~\ref{tbl:gzh_numbers}).

@@

The project includes images from the SDSS \citep{yor00,str02}, in particular
those from Data~Release~7 \citep{aba09}. A small number of images were used in
the creation of simulated \hst{} images, described in Sections
\ref{ssec:ferengi} and \ref{sec:debiasing} below; the majority of SDSS images
used in GZH were from Stripe~82. The Stripe~82 samples in GZH include
single-epoch and co-added images. The single-epoch images provide a local
sample for comparison to higher-redshift galaxies (including the new
measurements of clumpy structure), while the co-added images allow for analysis
of morphological properties as a function of image depth.

@@

Images with simulated AGN were classified in the interface in an identical
manner and evenly distributed with unaltered images of the galaxies.
Volunteers were not explicitly told that the images had been altered during
classification, as the goal was to measure the effect on normal classifications
using the same technique as closely as possible. Following classification, a
classifier could view a page with additional details about each galaxy; where
applicable, these pages contained further information regarding image
modifications. \citet{sim13} uses the simulated AGN host galaxy images for
more reliable identification of bulgeless galaxies hosting AGN in SDSS data.

@@

In addition to the physical parameters of the input images, the \ferengi{}
output depends on assumptions of the global galaxy evolution model. This
evolution is a crude mechanism that mimics the brightness increase of galaxies
with increasing redshift \citep[\eg,][]{lil98,lov12}. The effect on the
redshifted images is simply an empirical addition to the magnitude of a galaxy
of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
$e$ is the evolutionary correction in magnitudes ($e=-1$ essentially
brightens the entire galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
of the effects of ``losing'' spiral/disk features with increasing redshift
for two galaxies with no evolution corrections ($e=0$); as the signal-to-noise ratio in the images
decreases and the galaxies become fainter, the contrast between features
like spiral arms goes down and \ffeatures{} drops to the point where both
galaxies would have been classified as likely ellipticals.

@@

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. A
high-quality spectroscopic redshift in the ACS-GC is the primary option,
provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC
\citep{car10} catalogs and used in that order. For galaxies with multiple
spectroscopic redshifts, more than 98\% are consistent ($\Delta z<0.001$), and
so the order of selection made no practical difference. Galaxies with
inconsistent spectroscopic redshifts between any pair of catalogs are marked
with a flag in Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were
available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST,
MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
estimated redshift with the smallest error. 
%Table~\ref{tbl:redshifts} shows the results of this selection.

@@

Classifications were aggregated and weighted only if the classifier was logged
into GZH under their username (which was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous'' and receive the same $w=1$ weighting as the vast majority
of logged-in classifiers.
% We should also try to estimate how many anonymous classifiers there were, if possible. 
% Not clear that I can do that given the SQL data

@@

In GZH, the redshift range is large enough that cosmological evolution of the
types and morphologies of galaxies is expected for the \hst{} sample. In
addition, the effects of band shifting will change the images even more across
these redshift ranges. As a result, the previous methods of correcting for
redshift-dependent bias do not work.

@@

The unshaded regions in Figure~\ref{fig:f_vs_f} define discrete ranges of redshift,
surface brightness, and \ffeatures{} a galaxy must have in order for the
debiased correction to be confidently applied to a galaxy in the GZH sample.
While the appropriate correctable regions were defined discretely, the true
correctable region is assumed to be a smooth function of $z$, $\mu$, and
\ffeatures{}. To define this smooth space, we calculate the shape of the convex
hull that encloses the correctable and lower-limit \ferengi{} galaxies in
$z$-$\mu$-\ffeatures{} space. The boundaries are then adjusted until the
contamination from both groups is minimized. The resulting hulls define the
correctable and lower-limit regions for categorizing the \hst{} galaxies. The
results of this method and final categorization of the \hst{} sample are in
Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than
$z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased
since the relationship between \ffeaturesz{} and \ffeaturesrest{} is not
monotonic, and 56\% cannot be debiased since they either have an unknown
redshift or insufficient numbers of \ferengi{} images in their $z$-$\mu$ value
to determine a reliable value of $\zeta$.

@@

Few galaxies in the sample have sufficiently high corrections to completely
change them from being confidently ``smooth'' to ``featured'' following the
correction for redshift bias (Figure~\ref{fig:debiased_corrections}). As a
check, we compare morphologies of highly boosted galaxies to the expert visual
classifications in CANDELS \citep{kar15}.  Only nine galaxies that
were strongly boosted (\ffeatures$<0.25$ and \fbest$>0.50$) in GZH also
appear in the CANDELS expert sample. Of those, \citet{kar15}
classify 4 as spheroids/disky, 2 as disks, 1 as a spheroid, 1 as
irregular/disky and 1 as unclassifiable. The \fbest{} values for GZH are all
between 0.5 and 0.7, making them all intermediate disk candidates. Visual
inspection of the GZH images shows extended disk structure in at least
5~images; the remaining 4 are either extremely faint or have imaging artifacts
in the ACS data.  Since the surveys use different rest-frame filters and the
overlap sample is tiny, though, detailed comparisons between the overall
morphologies are highly difficult.

@@

The flexibility of this catalog allows users to set their own selection
criteria for vote fraction thresholds to create a morphologically pure sample.
Table~\ref{tbl:thresholds} provides baseline cuts for selecting galaxies of a
variety of morphologies. These thresholds are determined by a visual inspection
of subsamples. The thresholds used are a combination of 20~votes for the
task being considered, as well as limits on the vote fractions for previous
response(s) in the decision tree.

>>>>

\usepackage{color,soul}
\usepackage{deluxetable}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

\author[Willett et al.]{
Kyle W. Willett$^{1,2}$,
Melanie A. Galloway$^{1}$,
Steven P. Bamford$^{3}$,
Chris J. Lintott$^{4}$,
\newauthor
Karen L. Masters$^{5,6}$,
Claudia Scarlata$^{1}$,
B.D. Simmons$^{4,7}$\footnote{Einstein Fellow},
Melanie Beck$^{1}$,
\newauthor
Carolin N. Cardamone$^{8}$,
Edmond Cheung$^{9}$,
Edward M. Edmondson$^{5}$,
Lucy F. Fortson$^{1}$,
\newauthor
Roger L. Griffith$^{10,11}$,
Boris H\"au{\ss}ler$^{4,12,13}$,
Anna Han$^{14}$,
Ross Hart$^{3}$,
\newauthor
Thomas Melvin$^{5}$,
Michael Parrish$^{15}$,
Kevin Schawinski$^{16}$,
R.J. Smethurst$^{4}$,
\newauthor
Arfon M. Smith$^{4,15,17}$
\\
$^{1}$School of Physics and Astronomy, University of Minnesota, 116 Church St. SE, Minneapolis, MN 55455, USA \\
$^{2}$Department of Physics and Astronomy, University of Kentucky, 505 Rose St., Lexington, KY 40506, USA \\
$^{3}$School of Physics and Astronomy, The University of Nottingham, University Park, Nottingham, NG7 2RD, UK \\
$^{4}$Oxford Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK \\
$^{5}$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
$^{6}$SEPnet, South East Physics Network, UK \\
$^{7}$Center for Astrophysics and Space Sciences, Department of Physics, University of California, San Diego, CA 92093, USA \\
$^{8}$Department of Mathematics and Science, Wheelock College, Boston, MA 02215, USA \\
$^{9}$Kavli Institute for the Physics and Mathematics of the Universe (WPI), \\ Todai Institutes for Advanced Study, The University of Tokyo, Kashiwa 277-8583, Japan \\
$^{10}$Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA \\
$^{11}$Department of Astronomy \& Astrophysics, 525 Davey Lab, The Pennsylvania State University, University Park, PA 16802, USA \\
$^{12}$Centre for Astrophysics, Science \& Technology Research Institute, University of Hertfordshire, Hatfield, AL10 9AB, UK \\
$^{13}$European Southern Observatory, Alonso de C\'ordova 3107, Vitacura, Casilla 19001, Santiago, Chile \\
$^{14}$Department of Astronomy, Yale University, New Haven, CT 06520, USA \\
$^{15}$Adler Planetarium, 1300 S. Lake Shore Drive, Chicago, IL 60605, USA \\
$^{16}$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland \\
$^{17}$GitHub
}

@@

\begin{abstract}
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various publicly-released \textit{Hubble Space Telescope}
Legacy programs conducted with the Advanced Camera for Surveys, with filters that probe
the rest-frame optical emission from galaxies out to $z\sim1$.  The bulk of the
sample is selected to have $m_{I814W}<23.5$, but goes as faint as
$m_{I814W}<26.8$ for deep images combined over 5~epochs. The median redshift of
the combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out
to $z\simeq4$. The GZH morphological data include measurements of both bulge-
and disk-dominated galaxies, details on spiral disk structure that relate to
the Hubble type, bar identification, and numerous measurements of clump
identification and geometry.  This paper also describes a new method for
calibrating morphologies for galaxies of different luminosities and at
different redshifts by using artificially-redshifted galaxy images as a
baseline. The GZH catalog contains both raw and calibrated morphological vote
fractions for $119,849$~galaxies, providing the largest dataset to date
suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
% Number = hubble + goods_shallow + stripe82_coadd
\end{abstract}

@@

The advent of larger telescopes sensitive to a full range of observing wavelengths
has revealed that the distribution and properties of galaxy morphology have
strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$
(roughly 6~Gyr after the Big Bang), many galaxies are still in the process of
assembling the baryonic mass required to reproduce the mature, coherent
structures seen in the present day. This growth occurs in a variety of
ways, including accretion of baryons from large-scale galactic filaments
onto halos via streaming, mergers of individual dark matter halos along with
their baryons, conversion of gas into stars through gravitational collapse and
star formation, etc. The process can also be slowed or even reversed via
feedback from stellar winds, supernovae, and active black holes.  Each of these
processes affects the galaxy morphology in different ways, and so an accurate
measurement of the demographics as a function of redshift provides an extremely
powerful observational constraint on the physics involved \citep[for recent
reviews see][]{but13,con14}.

@@

Space-based observatories, particularly the \hubble{} (\hst), have been
responsible for the bulk of imaging studies of high-redshift galaxies.
Observations of fields with very deep imaging
\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
providing the angular resolution to distinguish internal structure and
characterize the morphology. While these measurements are helped by the fact
that the angular diameter distance is relatively flat beyond $z>1$ in a flat
$\Lambda$CDM cosmology, the relevant angular scales are only of the order
$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
much of the structure for a Milky Way-sized galaxy out to moderately high
redshifts (at least distinguishing a disk from a bulge), but is limited for
more compact structures. Since the size of galaxies evolves as roughly
$r\propto(1+z)^{-1}$ \citep{mao98,law12a}, the compact sizes of high-redshift
galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
However, the public availability of more than $10^5$~galaxies in archival
imaging has generated a sample with the potential
for statistically-robust studies of galaxy demographics and evolution.

@@

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
    covered two separate fields in the northern and southern hemispheres: the Hubble
    Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
    \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South
    ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{}
    ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
    respectively. ACS imaging in GOODS fields used 4~filters -- F435W (\Bband),
    \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
    epoch varied by band, from 1050--2100~seconds. The \Bband{} images were completed
    in a single epoch at the beginning of the survey, but the \Vband, \iband, and
    \zband{} images were taken in five separate epochs separated by 40--50~days
    each. GZH includes co-added images from GOODS at both 2-epoch and 5-epoch
    depths. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
    $5\sigma$ limiting magnitude for extended sources was 25.7 for \Vband{} and
    25.0 for \iband.

@@

%Selection of galaxies from these samples is described in Section \ref{ssec:galselect} below. 
In the ACS-GC \citep{gri12}, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS \& COSMOS, GEMS \&
GOODS-S (2-epoch), and GOODS-N (2-epoch) surveys, respectively. The full-depth
GOODS images from both fields included galaxies with $m<26.8$. This yielded a
total of $119,849$~images (Table~\ref{tbl:gzh_numbers}).

@@

The GZH project also includes images from the SDSS \citep{yor00,str02}, in particular
those from Data~Release~7 \citep{aba09}. A small number of images were used in
the creation of simulated \hst{} images, described in Sections
\ref{ssec:ferengi} and \ref{sec:debiasing} below. The majority of SDSS images
used in GZH were from Stripe~82, including both
single-epoch and co-added images. The single-epoch images provide a local
sample for comparison to higher-redshift galaxies (including the new
measurements of clumpy structure), while the co-added images allow for analysis
of morphological properties as a function of image depth.

@@

Images with simulated AGN were classified in the interface in an identical
manner and were evenly distributed with unaltered images of the galaxies.
Volunteers were not explicitly told that the images had been altered during
classification, as the goal was to measure the effect on normal classifications
using the same technique as closely as possible. Following classification, a
classifier could view a page with additional details about each galaxy; where
applicable, these pages contained further information regarding image
modifications. \citet{sim13} uses the simulated AGN host galaxy images for
more reliable identification of bulgeless galaxies hosting AGN in SDSS data.

@@

In addition to the physical parameters of the input images, the \ferengi{}
output depends on assumptions of the global galaxy evolution model.
This evolution is parameterized by a crude model that mimics the brightness increase of galaxies
with increasing redshift \citep[\eg,][]{lil98,lov12}. The effect on the
redshifted images is simply an empirical addition to the magnitude of a galaxy
of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
$e$ is the evolutionary correction in magnitudes ($e=-1$ essentially
brightens the entire galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
of the effects of ``losing'' spiral/disk features with increasing redshift
for two galaxies with no evolution corrections ($e=0$); as the signal-to-noise ratio in the images
decreases and the galaxies become fainter, the contrast between features
like spiral arms goes down and \ffeatures{} drops to the point where both
galaxies would have been classified as likely ellipticals.

@@

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. A
high-quality spectroscopic redshift in the ACS-GC is the primary option,
provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC
\citep{car10} catalogs and used in that order. For galaxies with multiple
spectroscopic redshifts, more than 98\% are consistent ($\Delta z<0.001$), and
so the order of selection made no practical difference. Galaxies with
inconsistent spectroscopic redshifts between any pair of catalogs are marked
with a flag in Table~\ref{tbl:catalog_hst}.  If no spectroscopic redshifts were
available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST,
MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data were used. The
measurement with the smallest reported 1-$\sigma$ error was selected in each
case.
%Table~\ref{tbl:redshifts} shows the results of this selection.

@@

Classifications for GZH were weighted only if the classifier was logged
into the site under their username (this was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous'' and receive the same $w=1$ weighting as the vast majority
of logged-in classifiers.
% We should also try to estimate how many anonymous classifiers there were, if possible. 
% Not clear that I can do that given the SQL data

@@

Instead, in GZH the redshift range is large enough that cosmological evolution of the
types and morphologies of galaxies is expected for the \hst{} sample. In
addition, the effects of band shifting will change the images even more across
these redshift ranges. As a result, the previous methods of correcting for
redshift-dependent bias do not work.

@@

The unshaded regions in Figure~\ref{fig:f_vs_f} define discrete ranges of redshift,
surface brightness, and \ffeatures{} within which a galaxy must lie in order for the
debiased correction to be confidently applied.
While the appropriate correctable regions were defined as discrete bins, the true
correctable region is assumed to be a smooth function of $z$, $\mu$, and
\ffeatures{}. To define this smooth space, we calculate the shape of the convex
hull that encloses the correctable and lower-limit \ferengi{} galaxies in
$z$-$\mu$-\ffeatures{} space. The boundaries are then adjusted until the
contamination from both groups is minimized. The resulting hulls define the
correctable and lower-limit regions for categorizing the \hst{} galaxies. The
results of this method and final categorization of the \hst{} sample are in
Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than
$z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased
since the relationship between \ffeaturesz{} and \ffeaturesrest{} is not
monotonic, and 56\% cannot be debiased since they either have an unknown
redshift or insufficient numbers of \ferengi{} images in their $z$-$\mu$ bin
to determine a reliable value of $\zeta$.

@@

Few galaxies in the sample have sufficiently high corrections to completely
change them from being confidently ``smooth'' to ``featured'' following the
correction for redshift bias (Figure~\ref{fig:debiased_corrections}). As a
check, we compare morphologies of highly boosted galaxies to the expert visual
classifications in CANDELS \citep{kar15}.  Only nine galaxies that
were strongly boosted (\ffeatures$<0.25$ and \fbest$>0.50$) in GZH also
appear in the CANDELS expert sample. Of those, \citet{kar15}
classify 4 as spheroids/disky, 2 as disks, 1 as a spheroid, 1 as
irregular/disky and 1 as unclassifiable. The \fbest{} values for GZH are all
between 0.5 and 0.7, making them all intermediate disk candidates. Visual
inspection of the GZH images shows extended disk structure in at least
5~images; the remaining 4 are either extremely faint or have imaging artifacts
in the ACS data.  Since the surveys use different rest-frame filters and the
overlap sample is tiny, though, detailed comparisons between the overall
morphologies are highly difficult (see
Sections~\ref{ssec:comparisons}--\ref{ssec:gzh_gzc}).

@@

The flexibility of this catalog allows users to set their own selection
criteria for vote fraction thresholds to create a morphologically pure sample.
Table~\ref{tbl:thresholds} provides suggested cuts for selecting galaxies with a
variety of morphologies. These thresholds were determined by visual inspection
of various subsamples of GZH data. The thresholds employ a combination of 20~votes for the
task being considered, as well as limits on the vote fractions for previous
response(s) in the decision tree.
